Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-10-30 paper/paper.Rmd
switched closure side with bins

  # Determine which bin the case falls in
  if(feature_value < feature_bin_cuts$Q25){
    feature_bin <- "lower"
  } else if (feature_bin_cuts$Q25 <= feature_value & feature_value < feature_bin_cuts$Q50){
    feature_bin <- "lower middle"
  } else if (feature_bin_cuts$Q50 <= feature_value & feature_value < feature_bin_cuts$Q75){
    feature_bin <- "upper middle"
  } else if (feature_bin_cuts$Q75 <= feature_value){
    feature_bin <- "upper"
  }

@@

  # Join the data and the explanations and edit and add additional variables
  hamby224_test_explain <- hamby224_test %>%
    mutate(case = as.character(case)) %>%
    full_join(hamby224_explain, by = "case") %>%
    mutate(case = factor(case),
           set = factor(set),
           bullet1 = factor(bullet1),
           bullet2 = factor(bullet2),
           land1 = factor(land1),
           land2 = factor(land2)) %>%
    mutate(mypred = rep(predict(rtrees, hamby224_test %>% select(rf_features), 
                                type = "prob")[,2], each = 3)) %>%
    select(case:rfscore, mypred, samesource:prediction) %>%
    mutate(feature_desc = factor(feature_desc),
           feature = factor(feature)) %>%
    mutate(feature_number = readr::parse_number(feature_desc),
           strictly_less = FALSE)

@@

  # Reorder the variable of feature_desc for plotting purposes
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(feature_desc = reorder(feature_desc, strictly_less),
           feature_desc = reorder(feature_desc, feature_number),
           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value)) %>%
    select(case:feature_desc, feature_number:feature_bin, data, prediction)

>>>>

  # Determine which bin the case falls in
  if(feature_value <= feature_bin_cuts$Q25){
    feature_bin <- paste("lower", feature, "bin")
  } else if (feature_bin_cuts$Q25 < feature_value & feature_value <= feature_bin_cuts$Q50){
    feature_bin <- paste("lower middle", feature, "bin")
  } else if (feature_bin_cuts$Q50 < feature_value & feature_value <= feature_bin_cuts$Q75){
    feature_bin <- paste("upper middle", feature, "bin")
  } else if (feature_bin_cuts$Q75 < feature_value){
    feature_bin <- paste("upper", feature, "bin")
  }

@@

  # Join the data and the explanations and edit and add additional variables
  hamby224_test_explain <- hamby224_test %>%
    mutate(case = as.character(case)) %>%
    full_join(hamby224_explain, by = "case") %>%
    mutate(case = factor(case),
           set = factor(set),
           bullet1 = factor(bullet1),
           bullet2 = factor(bullet2),
           land1 = factor(land1),
           land2 = factor(land2)) %>%
    mutate(mypred = rep(predict(rtrees, hamby224_test %>% select(rf_features), 
                                type = "prob")[,2], each = 3)) %>%
    select(case:rfscore, mypred, samesource:prediction) %>%
    mutate(feature_desc = factor(feature_desc),
           feature = factor(feature)) %>%
    mutate(feature_number = readr::parse_number(feature_desc),
           strictly_less = FALSE) %>%
    mutate(feature_bin = mapply(bin_labeller, feature = feature, feature_value = feature_value))

@@

  # Reorder the variables of feature_desc and feature_bin for plotting purposes
  hamby224_test_explain <- hamby224_test_explain %>%
    mutate(feature_desc = reorder(feature_desc, strictly_less),
           feature_desc = reorder(feature_desc, feature_number),
           feature_desc = reorder(feature_desc, as.numeric(feature))) %>%
    select(case:feature_desc, feature_number:feature_bin, data, prediction)
